Dynamics Analysis: The Sound of Teaching Music 1

### 2021-06-20 experiment-1/analysis/stats/dynamics.Rmd
tweak notes
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

- Order analysis (teaching/performing first?)
  + [All](#vel_dyn_order_group_all)

@@

- Order analysis (teaching/performing first?)
  + [All](#vel_diff_dyn_order_group_all)

@@

### Plot
#### Scatter plot
- Error bars show SEM of the mean

@@

### Plot
#### Line graph
- Error bars show SEM of the mean

>>>>

@@

@@

### Plot
#### Scatter plot
- Error bars show SEM of the mean.

@@

### Plot
#### Line graph
- Error bars show SEM of the mean.
